First paper - Draft

### 2017-06-20 paper/paper.Rnw
Added PISA variance across years graph

\section{Descriptives}

@@

@@

Large inequalities in parent's education leads to large inequalities in children's education (Breen & Jonsson 2007)

\section{Research design}

Make sure PISA variation is constant over time
\end{document}

>>>>

\section{Methods}

\subsection{Data}

\subsection{Data analysis}

\subsection{Descriptives}

@@

<<variance_pisa>>=

var_years <-
  map(adapted_year_data, function(.x) {
  .x %>%
  transmute(avg_cogn = matrixStats::rowMedians(as.matrix(select(.x, matches("^PV*.MATH$"))))) %>%
  summarize(var = sd(avg_cogn, na.rm = T),
            var_of_var = ) %>%
  pull(var)
})

enframer <- function(df) {
  df %>%
    enframe() %>%
    unnest()
}

var_years %>%
  setNames(seq(2000, 2015, 3)) %>%
  enframer() %>%
  ggplot(aes(name, value)) + geom_col()
@
\subsection{Results}

@@

\end{document}
